---
title: "hw02"
author: "Hao Wang"
output: github_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE, fig.path = '../images/')
load('hw02.Rdata')
```

```{r}
library(dplyr)
library(ggplot2)
```

```{r}
dat %>% 
  group_by(name) %>%
  summarise(number_of_shots = n()) %>%
  arrange(number_of_shots)
```

```{r}
dat %>% 
  group_by(name) %>%
  summarise(total = n(),
            made = sum(shot_made_flag == "made shot"),
            perc_made = made / total) %>%
  arrange(desc(perc_made))
```

```{r}
dat %>% 
  group_by(name) %>%
  summarise(total = sum(shot_type == "2PT Field Goal"),
            made = sum(shot_made_flag == "made shot" & shot_type == "2PT Field Goal"),
            perc_made = made / total) %>%
  arrange(desc(perc_made))
```

```{r}
dat %>% 
  group_by(name) %>%
  summarise(total = sum(shot_type == "3PT Field Goal"),
            made = sum(shot_made_flag == "made shot" & shot_type == "3PT Field Goal"),
            perc_made = made / total) %>%
  arrange(desc(perc_made))
```

```{r}
dp <- dat %>% 
  group_by(shot_distance) %>%
  summarise(made_shot_prop = sum(shot_made_flag == "made shot") / n() ) %>%
  arrange(shot_distance)
dp
```

```{r}
ggplot(data = dp) + geom_point(aes(x = shot_distance, y = made_shot_prop))
```


> What do you observe?

#### When the distance to the busket is small enough, the shot_prop is considerablly high comparing with the other data. However, within certain range of shot distance arount 3 to 35, there does not exist any obvious relationship or pattern between shot distance and made shot prop. When the distance is above around 35, almost all of made shot prop are zero except an extrem value that equals to 1.

> Can you confirm that the shorter the distance, the more effective the shots?

#### No, I cannot. For different ranges of value of shot distance, the diagram shows different situations and we cannot conclude any comprehensive pattern from the graph.

> Can you guesstimate a distance threshold beyond which the chance of making a
successful shot is basically null?

#### around 34 to 35

> What distances tend to have a percentage (of making a shot) of 50% or more?

#### the approximately qualified interval is [0, 2]

```{r}
dat_2 <- dat %>% 
  group_by(name, minute) %>%
  summarise(total_number_of_shots = n())

ggplot(data = dat_2) + 
  geom_point(aes(x = minute, y = total_number_of_shots), color = "cornflowerblue") +
  facet_wrap(~ name) +
  geom_path(aes(x = minute, y = total_number_of_shots), color = "cornflowerblue", alpha = 0.5) +
  theme_minimal()+
  geom_rect(xmin = 1, xmax = 12, ymin = 0, ymax = 100, alpha = 0.005) +
  geom_rect(xmin = 24, xmax = 36, ymin = 0, ymax = 100, alpha = 0.005) +
   scale_x_continuous()

```
